\TheTitle

### 2016-04-22 linvis.tex
Editing Discussion

Our goal was to build a tool to enable maintainers to effectively navigate and
pull explanation of the changes performed to the kernel over the period of a
release. Achieving this goal includes removing information that does not
pertain to given users. In figure \ref{fig:dag_view} and figure
\ref{fig:tree_view}, we can visually compare the results returned from gitk and
our tool for the top-level merge ``042dd60ca6dec9a02cefa8edd67de386e35755d6''
from kernel version 3.10. The relevant information in both of these figures is
identical, but the presentation drastically changes our ability to comprehend
what we are seeing. The primary difference is the removal of irrelevant
information. In gitk (\ref{fig:dag_view}), the visualization results include
commits and merges from other components of the kernel, while our tool
(\ref{fig:tree_view}) only includes the results that are specific to the
component of the kernel that we are interested in.

@@

The front-end uses asynchronous requests to gather the information for the trees and
tables. This enables third-parties to implement new front-ends, trying other
designs, though this interface may change in the future. The tree, file, and module
information is accessible through 
http://li.turingmachine.org/data/tree/JSON/\verb|<commit id>|,
http://li.turingmachine.org/data/files/JSON/\verb|<commit id>|,
http://li.turingmachine.org/data/modules/JSON/\verb|<commit id>|, respectively.

@@

\begin{tabular}{ccl}
        Field name & Data type & Description\\\hline
        cid & string & Commit id\\
        name & string & One-line log preview\\
        mlinus & string & Root merge commit id\\
        author & string & Author name and email\\
        mnext & string & Parent merge commit id\\
        children & object & Object of tree objects\\
\end{tabular}

@@

\begin{itemize}
        \item ``cid'': string, commit id
        \item ``files'': list, list of tuples in the format
                \begin{enumerate}
                        \item Filename: string
                        \item Lines added: unsigned integer
                        \item Lines removed: unsigned integer
                \end{enumerate}
        \item ``mnext'': string, the commit id of the next merge toward the
                top-level merge
        \item ``children'': list, List of all child objects with the same
                fields. Null if no children.
\end{itemize}

>>>>

Our goal was to build a tool to enable maintainers to effectively navigate and pull
explanation of the changes performed to the kernel over the period of a release.
Achieving this goal includes removing information that does not pertain to the area
of the kernel that the user is interested in. In figure \ref{fig:dag_view} and
figure \ref{fig:tree_view}, we can visually compare the results returned from gitk
and our tool for the top-level merge ``042dd60ca6dec9a02cefa8edd67de386e35755d6''
from kernel version 3.10. The relevant information to this commit in both of these
figures is identical, but the presentation drastically changes our ability to
comprehend what we are seeing. The primary difference is the removal of irrelevant
information. In gitk (\ref{fig:dag_view}), the visualization results include commits
and merges from other components of the kernel, while our tool (\ref{fig:tree_view})
only includes the results that are specific to the component of the kernel that we
are interested in.

@@

The front-end uses asynchronous requests to gather the information for the trees and
tables. This enables third-parties to implement new front-ends, trying other
designs, though this interface may change in the future. The tree, file, and module
information is accessible through
http://li.turingmachine.org/data/tree/JSON/\verb|<cid>|,
http://li.turingmachine.org/data/files/JSON/\verb|<cid>|,
http://li.turingmachine.org/data/modules/JSON/\verb|<cid>|, respectively.

@@

\begin{tabular}{ccl}
        Field name      & Data type & Description\\\hline
        \verb|cid|      & string    & Commit id\\
        \verb|name|     & string    & One-line log preview\\
        \verb|mlinus|   & string    & Root merge commit id\\
        \verb|author|   & string    & Author name and email\\
        \verb|mnext|    & string    & Parent merge commit id\\
        \verb|children| & object    & Object of tree objects\\
\end{tabular}

@@

\begin{tabular}{lll}
        Field name & Data type & Description\\\hline
        \verb|cid| & string & Commit id\\
        \verb|mnext| & string & Parent merge commit id\\
        \verb|children| & list & List of tree objects\\
        \verb|files| & list of tuples&
        \footnotesize{
        \begin{tabular}{lc}
                \verb|Filename| & String\\
                \verb|Lines added| & uint\\
                \verb|Lines removed| & uint\\
        \end{tabular}}\\
\end{tabular}
